What to Expect with Life Expectancy?

### 2024-12-04 paper/paper.qmd
Add files via upload

---
title: "What to Expect with Life Expectancy?"
subtitle: "Examining How Healthcare Expenditure, Education, and Medical Infrastructure Influence Life Expectancy Across Developed and Developing Regions"
author: 
  - Manjun Zhu
thanks: "Code and data are available at: [https://github.com/Karrrrmen/Life_Expectancy](https://github.com/Karrrrmen/Life_Expectancy)."
date: today
date-format: long
abstract: "Life expectancy has seen unprecedented growth in recent decades, driven by advancements in healthcare, improved access to medical services, and reduced child mortality. However, this growth has not been evenly distributed across the globe, with wealthier nations benefiting disproportionately. This research examines the impact of a nation’s educational standing and health conditions on life expectancy, exploring potential variables beyond those traditionally studied. By developing a linear model, the analysis identifies key relationships between education and healthcare indicators and their influence on population longevity. The findings aim to inform health policy and education planning, providing actionable insights to address disparities and promote equitable growth in life expectancy worldwide."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "What to Expect with Life Expectancy?"
subtitle: "Examining How Healthcare Expenditure, Education, and Medical Infrastructure Influence Life Expectancy Across Developed and Developing Regions"
author: 
  - Manjun Zhu
thanks: "Code and data are available at: [https://github.com/Karrrrmen/Life_Expectancy](https://github.com/Karrrrmen/Life_Expectancy)."
date: today
date-format: long
abstract: "Life expectancy has seen unprecedented growth in recent decades, driven by advancements in healthcare, improved access to medical services, and reduced child mortality. However, this growth has not been evenly distributed across the globe, with wealthier nations benefiting disproportionately. This research examines the impact of a nation’s educational standing and health conditions on life expectancy, exploring potential variables beyond those traditionally studied. By developing a linear model, the analysis identifies key relationships between education and healthcare indicators and their influence on population longevity. The findings aim to inform health policy and education planning, providing actionable insights to address disparities and promote equitable growth in life expectancy worldwide."
format: pdf
number-sections: true
bibliography: references.bib
---
